Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-11 docs/thesis/chapters/4_tensor_dl/tensor_dl.tex
initing tensor-dl

Compressive sensing is emergent for signal processing and hás been applied to Fields such as signal restoration, image processing and classification (sparce representation classification src )

Iterative dictionary learning hás been used as a blind technique for feature extraction, improving classification without require feature selection or principal conponent analysis

Big data analytics require techniques to Deal with multidimensional data, making Sense of strucutre and relationship of many dimensios. Pca is commonly adopted for dimensionality reduction and feature extraction. Tensor hás been adopted for multidimensional data analysis and can be explored for dictionary learning

Adaptive techniques for high dimensional and high thoughput

we propose to apply the tensor deconposition for dictionary learning in order to evidentiate the discriminative sensing of a fraud detection dataset

Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:

Dictionaries are either available analytically, or can be learned from a suitable training set. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

In some applications the data and its dictionary are multidimensional, e.g., when estimating jointly behavior of users in social networks. Computing tensor decompositions of multi-way datasets is particularly useful to extract hidden patterns and structure in multidimensional data analytics problems \cite{kolda2009tensor}. Tensor-based algorithms for dictionary learning can improve the performance for cases of multidimensional and separable data, regarding the dictionary identification rating, the required number of training samples and iterations for the optimization problem \cite{roemer2014tensor}.

In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks. The crucial idea is to allow the dictionary to have a separable structure, where separable means that the dictionary D is given by the Kronecker product of two smaller dictionaries A ∈ R h×a and B ∈ R w×b

% Without loss of generality we choose square image patches with w = h = 8, which is in accordance to the patch-sizes mostly used in the literature

Multidimensional parameter estimation and learning multidimensional separable dictionaries are growing research problems. Roemer \emph{et al.} \cite{roemer2014tensor} show that the multidimensional dictionary estimation problem can be efficiently formulated in terms of tensors, and that their results outperform existing schemes by exploiting the multilinear structure of the problem.

Existing dictionary learning schemes can be applied to multidimensional analysis and obtain valuable results. However, the performance of tensor-based algorithms for recovering of a known separable dictionary outperform existing schemes when dealing with growing multidimensional datasets, as can be seen in Figures \ref{fig:fig1} and \ref{fig:fig2}, which show that the recovering rating of traditional algorithms decreases over the dataset increasing.

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=12cm]{figures/5_20_2000_1000_100.eps}
     \caption{Matrix of 1.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig1}
\end{figure}

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=12cm]{figures/5_20_2000_24000_100.eps}
     \caption{Matrix of 24.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig2}
\end{figure}

Figures \ref{fig:fig1} and \ref{fig:fig2} show the evaluation of tensor-based and traditional dictionary learning algorithms for dictionary reconstruction of a multidimensional and separable data. Figure \ref{fig:fig1} presents the results for dictionary reconstruction from a matrix of 1000 elements by 50 atoms, while Figures \ref{fig:fig2} presents the results from a matrix with 24000 entries by 300 atoms. It is possible to observe better reconstruction rating for tensor-based algorithms.

Imbalanced data...
Recent developments in science and technology have enabled the growth and availability of raw data to occur at an explosive rate. This has created an immense opportunity for knowledge discovery and data engineering research to play an essential role in a wide range of applications from daily civilian life to national security. However, the high availability of raw data increases the challenges related to big data analytics and to imbalanced data, which corresponds to data sets exhibiting significant imbalances of classes or rare events of some classes. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms

@@

\section{Related Works}

@@

@@

\section{Data Model}

@@

\section{Proposed Approach}

@@

\section{Experiments}

@@

\section{Conclusion}

>>>>

% Compressed Sensing | Dictionary Learning | Multidimensional data | Tensor DL and Separable dictionaries

Compressed Sensing (CS) aims to obtain the most relevant information of a dataset, what makes it useful for compression, signal reconstruction, image processing and classification, such as in sparce representation classification (SRC) problems.

Dictionary learning is related to CS but seeks to obtain compact and meaningful signal representations, known as dictionary, from learning algorithms or models. DL is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. DL is based on the principle that some observations can be described by a sparse subset of atoms taken from a redundant dictionary, which represents the causes of some observations of the world. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

There are two major approaches for dictionary learning. First is the analytic approach, in which Discrete Cosine Transform basis, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary.

In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance.

In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

In some applications, the data and its dictionary are multidimensional, e.g., when estimating jointly behavior of users in social networks. Computing tensor decompositions of multi-way datasets is particularly useful to extract hidden patterns and structure in multidimensional data analytics problems \cite{kolda2009tensor}. Tensor-based algorithms for dictionary learning can improve the performance for cases of multidimensional and separable data, regarding the dictionary identification rating, the required number of training samples and iterations for the optimization problem \cite{roemer2014tensor}.

In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks.

Multidimensional parameter estimation and learning multidimensional separable dictionaries are growing research problems. The crucial idea about separable dictionaries is to allow the dictionary to have a separable structure, where separable means that the dictionary $\textbf{D}$ is given by the Kronecker product of two smaller dictionaries $\textbf{A} \in \mathbb{R}^{h \times a}$ and $\textbf{B} \in \mathbb{R}^{w \times b}$, for example. Roemer \emph{et al.} \cite{roemer2014tensor} show that the multidimensional dictionary estimation problem can be efficiently formulated in terms of tensors, and that their results outperform existing schemes by exploiting the multilinear structure of the problem.

Considering that big data problems require techniques to deal with multidimensional data in order to make sense of strucutre and relationship of many dimensions, and also considering that a key challenge to use sparse coding and dictionary learning for classification is how to find proper dictionaries and coefficients that highligh discriminative structure and relationships of one dataset, this work propose a tensor-based dictionary learning method for fraud detecton from imbalanced data, in order to apply the tensor deconposition for dictionary learning methods to evidentiate the discriminative sensing of a fraud detection dataset.

This chapter is organized as follows. Section \ref{sec:4_motivation} presents the motivation for the proposed work. In Section \ref{sec:4_relatedworks}, related works are discussed. Section \ref{sec:4_datamodel} presents the data model and the evaluated datasets. Section \ref{sec:4_proposal} describes the proposed approach for for fraud detecton from mobile money transacion. Section \ref{sec:2_experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:4_conclusion} draws the conclusions and the suggestions for future work.

\section{Motivation}
\label{sec:4_motivation}

Existing dictionary learning schemes can be applied to multidimensional analysis and obtain valuable results. However, the performance of tensor-based algorithms for recovering of a known separable dictionary outperform existing schemes when dealing with growing multidimensional datasets.

Considering that DL aims to obtain meaningful dictionaries, it is possible to evaluate DL algorithms by their performance to generate dictionaries that better represent one target data. Therefore, we can compare dictionary learning algorithms regarding recovering of a known dictionary.

A true dictionary of size 20x50 is made in each trial. A set of trainning data is made by using the true dictionary, each training vector is a sparse combination of some, here 5, vectors from the true dictionary and random noise. The number of training vectors can be chosen and the level of noise can be given. Then a dictionary is trained from the training set using one of the three methods, ILS-DLA (MOD), K-SVD, and RLS-DLA. The trained dictionary is then compared to the true dictionary, this is done by pairing the dictionaries atoms in the best possible way and using the angle between a true atom and a trained atom as a distance measure. The number of identified atoms is then found by comparing these angles to a limit, βlim.

Dictionary recovery problem

Figures \ref{fig:fig1} and \ref{fig:fig2} show the evaluation of tensor-based (K-HOSVD \cite{roemer2014tensor} and T-MOD \cite{roemer2014tensor}) and traditional dictionary learning algorithms (RLS-DLA \cite{skretting2010recursive}, K-SVD \cite{aharon2006rm} and MOD \cite{engan1999method}) for dictionary reconstruction of a multidimensional and separable data.

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=10cm]{figures/5_20_2000_1000_100.eps}
     \caption{Matrix of 1.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig1}
\end{figure}

Figure \ref{fig:fig1} presents the results for dictionary reconstruction from a matrix of 1000 elements by 50 atoms. We see that the RLS-DLA method here performs better than ILS-DLA (MOD) and K-SVD which both perform quite similar. The most remarkable difference is that RLS-DLA is able to identify all atoms for a quite small angle βlim. ILS-DLA (MOD) and K-SVD always have some atoms that are far away from the true atom. Having βlim=8.11 degrees corresponds to the case where the inner product of the two compared atoms is equal to 0.99, each atom has 2-norm equal to 1.

Figure \ref{fig:fig2} presents the results from a matrix with 24000 entries by 300 atoms. It is possible to observe better reconstruction rating for tensor-based algorithms

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=10cm]{figures/5_20_2000_24000_100.eps}
     \caption{Matrix of 24.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig2}
\end{figure}

Imbalanced data...

Recent developments in science and technology have enabled the growth and availability of raw data to occur at an explosive rate. This has created an immense opportunity for knowledge discovery and data engineering research to play an essential role in a wide range of applications from daily civilian life to national security. However, the high availability of raw data increases the challenges related to big data analytics and to imbalanced data, which corresponds to data sets exhibiting significant imbalances of classes or rare events of some classes. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms

@@

OMP \cite{davis1997adaptive}

Specifically, we propose to apply a sparse representation based classification (SRC) method through learning a tensor-based dictionary and evaluate the reconstruction error for fraud classification of mobile money transactions. We propose to use tensor-based dictionary learning for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics.

\section{Related Works}
\label{sec:4_relatedworks}

@@

RLS-DLA \cite{skretting2010recursive}, K-SVD \cite{aharon2006rm} and MOD \cite{engan1999method}

T-MOD and K-HOSVD \cite{roemer2014tensor}

@@

\section{Data Model}
\label{sec:4_datamodel}

@@

\section{Proposed Approach}
\label{sec:4_proposal}

@@

\section{Experiments}
\label{sec:4_experiments}

@@

\section{Conclusion}
\label{sec:4_conclusion}
